---
documentclass: resumehp
fontsize: 9pt
geometry: margin=0.75in
urlcolor: NavyBlue
# https://en.wikibooks.org/wiki/LaTeX/Colors
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    keep_tex: yes
    template: hptemplate.tex
  html_document:
    df_print: paged
# rmdformats::html_clean:
#   highlight: kate
user_params:
  address1: Associate Professor, Graduate School of Data Science, Seoul National University
  address2: 43-505, 1 Gwanak-ro, Gwanak-gu, Seoul 08826, South Korea
  address3: \url{hyunwoopark@snu.ac.kr} | \url{https://hyunwoopark.com} | +82-2-880-9779
  address4: "Last updated: \\today"
  name: Hyunwoo Park
---

```{r, echo=F}
# knitr::opts_knit$get("out.format") # Not informative.
# knitr::opts_knit$get("rmarkdown.pandoc.to") # Works only if knit() is called via render(), i.e. when using the button in RStudio.
# knitr::opts_knit
# rmarkdown:::parse_yaml_front_matter(
#    readLines(knitr::current_input())
#    )$output
```
```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
# webcolor <- "#460507"
webcolor <- "black"
```

<!-- \begin{center} -->
<!-- Last updated: \today -->
<!-- \end{center} -->

# Experience

## Seoul National University, Seoul, South Korea
- Associate Professor, Graduate School of Data Science, 2021 -- Present
- Associate Dean for Academic Affairs, Graduate School of Data Science, 2023 -- 2025
- (Interim) Associate Dean for Student Affairs, Graduate School of Data Science, 2023 -- 2024

## The Ohio State University, Columbus, OH, USA
- Assistant Professor in Management Sciences, Fisher College of Business, 2017 -- 2021
- Core Faculty, Translational Data Analytics Institute, 2017 -- 2021

## Georgia Institute of Technology, Atlanta, GA, USA
- Postdoctoral Fellow, Tennenbaum Institute, 2015 -- 2017


# Education

## Georgia Institute of Technology, Atlanta, GA, USA
- Ph.D. in Industrial Engineering (Minor in Economics), 2015
- Dissertation: "Computational Analysis for Technological Innovation in Complex Enterprise Systems"
- Committee:
  - Co-chairs: William B. Rouse, Rahul C. Basole
  - Members: Leon F. McGinnis, Nicoleta Serban, Raul O. Chao (external; UVA Darden)

## University of California, Berkeley, CA, USA
- Master of Information Management and Systems (Management of Technology Certificate), 2010

## Seoul National University, Seoul, South Korea
- B.S. in Electrical Engineering (_summa cum laude_), 2008


# Selected Publications \hfill \begingroup\small \textnormal{Journal Lists: \href{https://jsom.utdallas.edu/the-utd-top-100-business-school-research-rankings/}{UTD24} | \href{https://www.ft.com/content/3405a512-5cbb-11e1-8f1f-00144feabdc0}{FT50} | \href{https://charteredabs.org/academic-journal-guide}{ABS}}\endgroup\hspace{-0.45in}
\vspace{.2em}
\begingroup\small ($^*$ denotes equal contribution among authors. For the full publication list, visit \url{https://hyunwoopark.com}.)\endgroup
\vspace{.5em}

\pubentry{[J38]}{Wang Y, Ball G, Anand G, \textbf{Park H}. 2025. Obligatory responses to FDA inspection outcomes and future drug shortages. \textit{Manufacturing \& Service Operations Management}, 27(3), pp.789-807 [\href{https://pubsonline.informs.org/doi/abs/10.1287/msom.2022.0322}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absthree}

\pubentry{[J37]}{Noh IJ, Gray J, Ball GP, Wright Z, \textbf{Park H}. 2025. Are All Generic Drugs Created Equal? An Empirical Analysis of Generic Drug Manufacturing Location and Serious Drug Adverse Events. \textit{Production and Operations Management}, 34(9), pp.2601-2617 [\href{https://journals.sagepub.com/doi/abs/10.1177/10591478251319691}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfour}

\pubentry{[J36]}{Heo S, Son S, \textbf{Park H}. 2025. HaluCheck: Explainable and verifiable automation for detecting hallucinations in LLM responses. \textit{Expert Systems with Applications}, 272(126712) [\href{https://www.sciencedirect.com/science/article/pii/S0957417425003343}{Link {\scriptsize\faExternalLink}}] \absgen}

\pubentry{[J35]}{Kim Y, \textbf{Park H}. 2025. Theorizing Critical Locus of Supply: A Material Flow Perspective. \textit{Journal of Supply Chain Management}, 61(4), pp.134-164 [\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/jscm.70008}{Link {\scriptsize\faExternalLink}}] \absfour}

\pubentry{[J32]}{Ball GP, Bavafa H, Blanco C, \textbf{Park H}, Wowak KD. 2024. Gender and Serious Drug Recalls: A Textual Sentiment Analysis of Drug Reviews on WebMD. \textit{Production and Operations Management}, 34(4), pp.698-710 [\href{https://journals.sagepub.com/doi/abs/10.1177/10591478241256644}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfour}

\pubentry{[J31]}{Basole RC, \textbf{Park H}, Seuss CD. 2024. Complex Business Ecosystem Intelligence Using AI-Powered Visual Analytics. \textit{Decision Support Systems}, 178, 114133 [\href{https://www.sciencedirect.com/science/article/pii/S0167923623002087}{Link {\scriptsize\faExternalLink}}] \absthree}

\pubentry{[J28]}{Lee J, Jung HJ, \textbf{Park H}. 2023. Rare is Beautiful? The Interplay Between Rareness, Technology Search, and Technology Value. \textit{Production and Operations Management}, 32(4), pp.1019-1040 [\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/poms.13908}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfour}

\pubentry{[J25]}{\textbf{Park H}, Blanco C, Bendoly E. 2022. Vessel Sharing and its Impact on Maritime Operations and Carbon Emissions. \textit{Production and Operations Management}, 31(7), pp.2925-2942 [\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/poms.13730}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfour}

\pubentry{[J24]}{Chopra S, \textbf{Park H}, Shim S. 2022. Extended Graph Formulation for the Inequity Aversion Pricing Problem on Social Networks. \textit{INFORMS Journal on Computing}, 34(3), pp.1327-1344 [\href{https://pubsonline.informs.org/doi/abs/10.1287/ijoc.2021.1148}{Link {\scriptsize\faExternalLink}}] \utd~\absthree}

\pubentry{[J23]}{Lee J, \textbf{Park H}, Zaggl M. 2022. When to Signal? Contingencies for Career-Motivated Contributions in Online Collaboration Communities. \textit{Journal of the Association for Information Systems}, 23(6), pp.1386-1419 [\href{https://aisel.aisnet.org/jais/vol23/iss6/8/}{Link {\scriptsize\faExternalLink}}] \absfourstar}

\pubentry{[J22]}{\textbf{Park H}. 2022. [Book Review] A History of Data Visualization and Graphic Communication. \textit{Journal of the American Statistical Association}, 117(539), pp.1601-1603 [\href{https://www.tandfonline.com/doi/abs/10.1080/01621459.2022.2098134}{Link {\scriptsize\faExternalLink}}] \absfour}

\pubentry{[J20]}{Basole RC, \textbf{Park H}. 2019. Interfirm Collaboration and Firm Value in Software Ecosystems: Evidence from Cloud Computing. \textit{IEEE Transactions on Engineering Management}, 66(3), pp.368-380 [\href{https://ieeexplore.ieee.org/document/8424065/}{Link {\scriptsize\faExternalLink}}] \absthree}

\pubentry{[J19]}{Basole RC, \textbf{Park H}, Chao RO. 2019. Visual Analysis of Venture Similarity in Entrepreneurial Ecosystems. \textit{IEEE Transactions on Engineering Management}, 66(4), pp.568-582 [\href{https://ieeexplore.ieee.org/document/8425782/}{Link {\scriptsize\faExternalLink}}] \absthree}

\pubentry{[J18]}{\textbf{Park H}, Bellamy MA, Basole RC. 2018. Structural Anatomy and Evolution of Supply Chain Alliance Networks: A Multi-Method Approach. \textit{Journal of Operations Management}, 63, pp.79-96 [\href{https://www.sciencedirect.com/science/article/pii/S0272696318300664}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfourstar}

\pubentry{[J17]}{Park BS, \textbf{Park H}, Ramanujam R. 2018. \textit{Tua Culpa}: When an Organization Blames its Partner for Failure in a Shared Task. \textit{Academy of Management Review}, 43(4), pp.792-811 [\href{https://journals.aom.org/doi/10.5465/amr.2016.0305}{Link {\scriptsize\faExternalLink}}] \utd~\ft~\absfourstar}

\pubentry{[J16]}{Basole RC, Srinivasan A, \textbf{Park H}, Patel S. 2018. ecoxight: Discovery, Exploration and Analysis of Business Ecosystems using Interactive Visualization. \textit{ACM Transactions on Management Information Systems}, 9(2), no. 6 [\href{https://dl.acm.org/citation.cfm?id=3185047}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[J14]}{Srinivasan A, \textbf{Park H}, Endert A, Basole RC. 2018. Graphiti: Interactive Specification of Attribute-based Edges for Network Modeling and Visualization. \textit{IEEE Transactions on Visualization and Computer Graphics}, 24(1), pp.226-235 [\href{http://ieeexplore.ieee.org/document/8019835/}{Link {\scriptsize\faExternalLink}}] \topcs}

\pubentry{[J13]}{Kim B-C, Lee J, \textbf{Park H}. 2017. Two-Sided Platform Competition with Multihoming Agents: An Empirical Study on the Daily Deals Market. \textit{Information Economics and Policy}, 41, pp.36-53 [\href{http://www.sciencedirect.com/science/article/pii/S0167624516300907}{Link {\scriptsize\faExternalLink}}] \absgen}

\pubentry{[J12]}{Basole RC$^*$, Bellamy MA$^*$, \textbf{Park H}$^*$. 2017. Visualization of Innovation in Global Supply Chain Networks. \textit{Decision Sciences}, 48(2), pp.288-306 [\href{http://onlinelibrary.wiley.com/doi/10.1111/deci.12213/abstract}{Link {\scriptsize\faExternalLink}}] \absthree}

\pubentry{[J11]}{\textbf{Park H}, Bellamy MA, Basole RC. 2016. Visual Analytics for Supply Network Management: System Design and Evaluation. \textit{Decision Support Systems}, 91, pp.89-102 [\href{http://www.sciencedirect.com/science/article/pii/S0167923616301397}{Link {\scriptsize\faExternalLink}}] [\href{http://visualscm.herokuapp.com/}{Live Demo {\scriptsize\faDesktop}}] \absthree}

\pubentry{[J10]}{\textbf{Park H}$^*$, Basole RC$^*$. 2016. Bicentric Diagrams: Design and Applications of a Graph-Based Relational Set Visualization Technique. \textit{Decision Support Systems}, 84, pp.64-77 [\href{http://www.sciencedirect.com/science/article/pii/S016792361630001X}{Link {\scriptsize\faExternalLink}}] [\href{http://bicentric.herokuapp.com/}{Live Demo {\scriptsize\faDesktop}}] \absthree}

\pubentry{[J9]}{Basole RC, Bellamy MA, \textbf{Park H}, Putrevu J. 2016. Computational Analysis and Visualization of Global Supply Network Risks. \textit{IEEE Transactions on Industrial Informatics}, 12(3), pp.1206-1213 [\href{https://ieeexplore.ieee.org/document/7445240/}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[J8]}{\textbf{Park H}, Lee J, Kim BC. 2015. Project Selection in NIH: A Natural Experiment from ARRA. \textit{Research Policy}, 44(6), pp.1145-1159 [\href{http://www.sciencedirect.com/science/article/pii/S0048733315000396}{Link {\scriptsize\faExternalLink}}] \ft~\absfourstar}

\pubentry{[J7]}{Basole RC, Braunstein M, Kumar V, \textbf{Park H}, Kahng M, Chau DHP, Tamersoy A, Hirsh DA, Serban N, Bost J, Lesnick B, Schissel BL, Thompson M. 2015. Understanding Variations in Pediatric Asthma Care Processes in the Emergency Department using Visual Analytics. \textit{Journal of the American Medical Informatics Association (JAMIA)}, 22(2), pp.318-323 [\href{http://jamia.oxfordjournals.org/content/22/2/318.abstract}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[J6]}{Basole RC, Russell MG, Hutamaki J, Rubens N, Still K, \textbf{Park H}. 2015. Understanding Business Ecosystem Dynamics: A Data-Driven Approach. \textit{ACM Transactions on Management Information Systems}, 6(2), no. 6 [\href{http://dl.acm.org/citation.cfm?id=2724730}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[J5]}{Basole RC, Qamar A, \textbf{Park H}, Paredis C, McGinnis LF. 2015. Visual Analytics for Early-Phase Complex Engineered System Design Support. \textit{IEEE Computer Graphics and Applications}, 35(2), pp.41-51 [\href{https://ieeexplore.ieee.org/document/7006349/}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[J4]}{Basole RC, \textbf{Park H}, Barnett BC. 2015. Coopetition and Convergence in the ICT Ecosystem. \textit{Telecommunications Policy}, 39(7), pp.537-552 [\href{http://www.sciencedirect.com/science/article/pii/S0308596114000627}{Link {\scriptsize\faExternalLink}}] \absgen}

\pubentry{[J1]}{\textbf{Park H}, Clear T, Rouse WB, Basole RC, Braunstein M, Brigham KL, Cunningham L. 2012. Multi-Level Simulations of Health Delivery Enterprises Flight Simulators for Policy, Strategy, Planning, and Management. \textit{Service Science}, 4(3), pp.253-268 [\href{http://pubsonline.informs.org/doi/abs/10.1287/serv.1120.0022}{Link {\scriptsize\faExternalLink}}] \absgen}

# Selected Referred Conference Proceedings
\vspace{.2em}
\begingroup\small (For the full list, visit \url{https://hyunwoopark.com}.)\endgroup
\vspace{.5em}

\pubentry{[C16]}{Lee D, Ju J, Song H, \textbf{Park H}. 2026. From Ballpark to Society: Understanding Stakeholders' Adaptation to Automated Judgment via ABS in Baseball. \textit{ACM CHI 2026} (Accepted)}

\pubentry{[C15]}{Kim J, Hwang Y, Kim M, Bae S, \textbf{Park H}. 2025. Spatio-Temporal Graphs Beyond Grids: Benchmark for Maritime Anomaly Detection. \textit{NeurIPS 2025 Workshop on AI for Science} [\href{https://arxiv.org/abs/2512.20086}{Link {\scriptsize\faExternalLink}}] \bestposter}

\pubentry{[C14]}{Deshmane A, \textbf{Park H}, Rahmani M. 2025. From Paychecks to Well-Being: Unpacking Drivers of Employee Turnover at Scale. \textit{INFORMS MSOM 2025}}

\pubentry{[C11]}{Kim J, Kim M, Ju J, Hwang Y, Lee W, \textbf{Park H}. 2025. Adaptive Sparsified Graph Learning Framework for Vessel Behavior Anomalies. \textit{AAAI 2025 Workshop on Anomaly Detection in Scientific Domains} [\href{https://www.nsfhdr.org/html/mlchallenge-y1/aaai-workshop2024.html}{Link {\scriptsize\faExternalLink}}]}

\pubentry{[C9]}{Choi Y, \textbf{Park H}. 2024. A Long-term, Geospatial-based Approach for Location Suitability Evaluation of Flood Relief Camps Considering Climate Change. \textit{INFORMS MSOM 2024}}

\pubentry{[C8]}{Choi Y, Kim Y, Lee CG, Park JJ, \textbf{Park H}. 2024. Revelio: A Lifelog Visualization System with Google My Activity. \textit{IEEE PacificVis 2024} \bestposter}

\pubentry{[C6]}{Lee J, Jung HJ, \textbf{Park H}. 2020. Rare is Beautiful? Rare Technological Resources and Value Implications. \textit{Academy of Management Best Paper Proceedings} [\href{https://journals.aom.org/doi/abs/10.5465/AMBPP.2020.175}{Link {\scriptsize\faExternalLink}}] \bestpaperfinalist}

\pubentry{[C2]}{\textbf{Park H}, Lee J. 2015. An (Almost) Free Lunch? Social Recognition and Knowledge Sharing Behavior in a Virtual Community. \textit{Academy of Management Best Paper Proceedings} [\href{https://journals.aom.org/doi/abs/10.5465/ambpp.2015.184}{Link {\scriptsize\faExternalLink}}] \beststudentpaper}

# Book Chapters and Technical Reports
\vspace{.5em}
- Ghemawat P, Altman SA. _DHL Global Connectedness Index 2014_. November 2014 (Chapter II: Visualizing Global Connectedness) 
\vspace{.5em}
- Glushko RJ. _Discipline of Organizing_. MIT Press. May 2013 (Chapter 9: Interactions with Resources)
\vspace{.5em}
- Dai JG, **Park H**. _Stochastic Manufacturing and Service Systems_. (Unpublished lecture notes)


# Awards, Grants, and Honors

## Awards and Honors

- **Distinguished Service Award**, _INFORMS Technology, Innovation Management and Entrepreneurship Section (TIMES)_, 2025
- Meritorious Reviewer Award, _INFORMS Journal on Computing_, 2025
- **Elected Member, Policy Studies Division**, _Young Korean Academy of Science and Technology (Y-KAST)_, 2024 -- Present
- **Best Paper Award Finalist**, _Academy of Management Operations & Supply Chain Management (OSCM) Division_, 2020
- **Best Dissertation Award Runner-up**, _INFORMS Technology, Innovation Management and Entrepreneurship Section (TIMES)_, 2017
- **Best Paper Award Winner**, _Academy of Management Organizational Communication & Information Systems (OCIS) Division_, 2017
- Honorable Mention, _13th Places & Spaces: Mapping Science_, 2017
- **Best Student Paper Award Winner**, _Academy of Management Technology & Innovation Management (TIM) Division_, 2015
- Dr. James R. Chen Award (Best Master’s project in one of three tracks), _School of Information, UC Berkeley_, 2010
- Excellence Award (1st place), Idea Competition awarded by _CEO of Samsung Electronics_, 2005
- Army Commendation Medal, _Department of the United States Army_, 2005
- **Presidential Scholar**, awarded by _President of the Republic of Korea_, 2002
- **Gold Medalist**, _33rd International Chemistry Olympiad_, 2001


## Fellowships

- Tennenbaum Institute Fellow, _Georgia Institute of Technology_, 2010-2017
- McLean Fellowship, _Georgia Institute of Technology_, 2013-2015
- Doctoral Fellow, _Systems Engineering Research Center_, 2014
- George Fellowship, Health Systems Institute, _Georgia Institute of Technology_, 2012
- John Morris Fellowship, _School of Industrial and Systems Engineering, Georgia Institute of Technology_, 2010-2012
- Doctoral Fellowship, _Korea Foundation for Advanced Studies_, 2010-2015
- Overseas Study Scholarship, _Samsung Foundation_, 2008-2010
- Undergraduate Fellowship, _Korea Foundation for Advanced Studies_, 2002-2008


## Grants
- **Co-PI**, _Korea NRF Human-in-the-Loop AI Decision-Making Algorithm and Policy_, 2025-2028
- **PI**, _Korea MSIT Generative AI Leading Talent Training R&D Program_, 2024-2027
- **PI**, _Korea MOF Vessel Trajectory Prediction and Anomaly Detection_, 2022-2025
- **Co-PI**, _Korea NRF Large-scale AI Model and Platform Optimization Center_, 2023-2026
- **PI**, _Korea NRF Emerging Scholar Program_ (Equivalent to NSF Career), 2022-2027
- **Co-PI**, _FDA Broad Agency Announcement (BAA) "FDA Quality Management and Pharmaceutical Firm Learning to Reduce Drug Quality Risks"_, 2019-2021
- **Co-PI**, _U01 Grant from FDA to NIPTE "Manufacturing Sector Research Initiative"_, 2018–2019
- Honorarium from Conference on Internet Search and Innovation, _Northwestern University_, 2013
- _NET Institute_ (Networks, Electronic Commerce, and Telecommunications) Grants for Summer 2012
- Research Promotion Grant, _Korea Science and Engineering Foundation_, 2002-2008



# Teaching Experience

## Seoul National University, Graduate School of Data Science
- Past Students
  - Ph.D.: Yunsu Kim (Samsung Electronics)
  - Master's: Byungwoo Kim (SK Hynix), Sejin Kim (National Police Agency), Ji Hong Min (Hanwha Ocean), Jeongjin Park (LG CNS), Sungwook Son (Intel), Seonggu Shin (IBM), Sojeong Yeon, Seungju Lee (Panirois), Chan Gyu Lee (ETRI), Changuk Lee (Hyundai Marine & Fire Insurance), Chansong Lim (Ph.D. Student @ UC Riverside), Yeeun Choi (Ernst & Young), Sangwoo Heo (Naver Future AI Center)
\vspace{.5em}
- Current Students: See \url{https://dial.snu.ac.kr/members/}
\vspace{.5em}
- Instructor
  - Veritas Practice: Data Visualization and Self-Reflection; AU24, SP26
  - Data Visualization for Medical Applications; SP24, SP26
  - Data Analysis and Visualization; AU21, AU22, AU23
  - Computing Foundations for Data Science; AU22, SP23

## The Ohio State University, Fisher College of Business
- Advising & Committee
  - In Joon Noh (Fisher), Committee Member, SP20 (Placement: Penn State University)
  - Rahul Pandey (Fisher), Committee Member, SP20 (Placement: University of Memphis)
  - Junpeng Wang (Computer Science), Committee Member, SP19 (Placement: VISA Research)
  - Yingchao Lan (Fisher), Committee Member, SP18 (Placement: University of Nebraska--Lincoln)
\vspace{.5em}
- Instructor
  - BM7331 Descriptive Analytics and Visualization; SP19, SP20
  - BM2320 Business Statistics; SP18, SP19, SP20
\vspace{.5em}
- Course Development
  - BM7331 Descriptive Analytics and Visualization; AU17–AU18

## Georgia Institute of Technology, School of Industrial and Systems Engineering
- Instructor, ISyE 3232 Stochastic Manufacturing and Service Systems (Undergraduate Core Stochastic Course), SU11, Average course evaluation rating: 4.4/5.0
- TA for Prof. Jim Dai, ISyE 3232, SP11

## UC Berkeley, School of Information
- TA for Prof. Robert Glushko, INFO 290-1 Information and Service System Design, SP09
- TA for Prof. John Chuang, INFO 206 Distributed Computing Applications and Infrastructure, AU09




# Professional Services

## Professional Membership
- International
  - Institute of Operations Research and Management Science (INFORMS) -- Senior Member
  - Association for Computing Machinery (ACM), Academy of Management (AOM), Decision Sciences Institute (DSI), Institute of Electrical and Electronics Engineers (IEEE), Industry Studies Association (ISA), Production and Operations Management Society (POMS)
- Korean: KASBA (Management), KDMS (Data Mining), KIIE (Industrial Engineering), KMIS (Information Systems), KOPOMS (Operations Management), KORMS (Operations Research and Management Science), KOSIME (Technology Management), KrAIS (Information Systems)

## Leadership
- AOM OSCM Regional Ambassador for Asia, 2025 -- Present
- INFORMS TIMES Past President, 2025
- INFORMS TIMES President, 2024
- INFORMS TIMES President-Elect, 2023
- INFORMS TIMES VP of Programs, 2022
- INFORMS TIMES VP of Membership and Communications, 2021

## Track Chair
- TIME/NPD Track for INFORMS Annual Meeting 2022
- NPD Track for INFORMS Annual Meeting 2021

## Session Chair
- INFORMS Annual Meeting 2017, 2019, 2020
- POMS Annual Meeting 2016, 2019

## Program Committee
- European Conference of Artificial Intelligence (ECAI), 2024-2025
- INFORMS MSOM Conference, 2024
- Pacific Asia Conference on Information Systems (PACIS), 2017

## University and Department Service
- Seoul National University
  - SNU College Curriculum Revision Subcommittee, 2026-2028
  - University Academic Affairs Committee, 2023-2025
  - University Research Committee, 2023-2024
  - AI-X Curriculum Committee, 2021-2023
  - Samsung Research-SNU Project Committee, 2022
  - Various Graduate School of Data Science Committees, 2021-2025
- The Ohio State University
  - Analytics Curriculum Committee, 2020-2021
  - Faculty Recruiting Committee, 2018

## Editorial Review Board
- Decision Sciences Journal (DSJ), 2022 -- Present
- Journal of Operations Management (JOM), 2022 -- Present

## Ad-hoc Reviewer
- **Journals**

  Decision Sciences Journal (DSJ), Decision Support Systems (DSS), European Journal of Operations Research (EJOR), IEEE Transactions on Engineering Management (TEM), IEEE Transactions on Visualization and Computer Graphics (TVCG), Industry and Innovation, Information & Management, INFORMS Journal on Computing (IJOC), International Journal on Human-Computer Interaction (IJHCI), International Journal of Production Research (IJPR), Journal of Business Logistics (JBL), Journal of International Business Studies (JIBS), Journal of Machine Learning Research (JMLR), Journal of Operations Management (JOM), Journal of Technology Transfer (JOTT), Journal of Supply Chain Management (JSCM), Production and Operations Management (POM), Research Policy (RP), Service Science, Strategic Management Journal (SMJ)

- **Conferences**

  Academy of Management Conference (AOM), ACM SIGCHI Conference (CHI), ACM SIGIR Conference (SIGIR), Decision Sciences Institute (DSI), Hawaii International Conference on System Sciences (HICSS), International Conference on Learning Representations (ICLR), IEEE Technology and Engineering Management Conference (TEMSCON), IEEE Visualization Conference (VIS), International Conference on Information Systems (ICIS)



# Invited Talks
\vspace{.5em}
- Goizueta Business School, Emory University, Atlanta, GA, USA, 2025
- Yonsei University School of Business, S. Korea, 2025
- Department of Industrial & Management Engineering, POSTECH, S. Korea, 2025
- School of Digital Humanities and Social Sciences, KAIST, S. Korea, 2024
- School of Electrical Engineering, Seoul National University, S. Korea, 2022
- Graduate School of Data Science, Seoul National University, S. Korea, 2021
- Department of Industrial Engineering, Seoul National University, S. Korea, 2020
- Department of Industrial and Systems Engineering, KAIST, S. Korea, 2019
- Yonsei University Business School, S. Korea, 2019
- Korea University Business School, S. Korea, 2018
- Department of Business and Technology Management, KAIST, S. Korea, 2018
- Graduate School of Convergence Science and Technology, Seoul National University, S. Korea, 2017
- Operations Research Group, IBM Thomas J. Watson Research Center, NY, USA, 2017
- Department of Computer Science and Engineering, The Ohio State University, OH, USA, 2017
- Fox School of Business, Temple University, Philadelphia, PA, USA, 2017
- Warwick Business School, University of Warwick, Coventry, UK, 2017
- Nanyang Business School, Nanyang Technological University, Singapore, 2017
- Fisher College of Business, The Ohio State University, Columbus, OH, USA, 2017
- E. J. Ourso College of Business, Louisiana State University, Baton Rouge, LA, USA, 2016
- College of Business, University of Illinois at Chicago, Chicago, IL, USA, 2016
- Graduate School of Convergence Science and Technology, Seoul National University, S. Korea, 2012



# Conference Presentations

## 2025
- AAAI Workshop on Anomaly Detection in Scientific Domains, Philadelphia, PA
- AOM Annual Meeting, Copenhagen, Denmark
- DRUID Conference, Toronto, Canada
- IEEE PacificVis, Taipei, Taiwan
- INFORMS Annual Meeting, Atlanta, GA
- INFORMS MSOM Conference, London, UK
- NeurIPS Workshop on AI for Science, San Diego, CA
- POMS Annual Meeting, Atlanta, GA

## 2024
- AOM Annual Meeting, Chicago, IL
- IEEE PacificVis, Tokyo, Japan
- INFORMS Annual Meeting, Seattle, WA
- INFORMS MSOM Conference, Minneapolis, MN

## 2023
- INFORMS Annual Meeting, Phoenix, AZ

## 2022
- INFORMS Annual Meeting, Indianapolis, IN

## 2020
- AOM Annual Meeting, Virtual
- DSI Annual Meeting, Virtual
- INFORMS Annual Meeting, Virtual

## 2019
- DSI Annual Meeting, New Orleans, LA
- INFORMS Annual Meeting, Seattle, WA
- PDA/FDA Joint Regulatory Conference, Washington, DC
- POMS Annual Meeting, Washington, DC
- Wharton People and Organizations Conference, Philadelphia, PA

## 2018
- INFORMS Annual Meeting, Phoenix, AZ
- POMS Annual Meeting, Houston, TX

## 2017
- AOM Annual Meeting, Atlanta, GA
- DRUID Conference, New York, NY
- DSI Annual Meeting, Washington, DC
- INFORMS Annual Meeting, Houston, TX
- POMS Annual Meeting, Seattle, WA
- Product and Service Innovation (PSI), Midway, UT

## 2016
- DSI Annual Meeting, Austin, TX
- INFORMS Annual Meeting, Nashville, TN
- Open and User Innovation (OUI) Conference, Boston, MA
- POMS Annual Meeting, Orlando, FL

## 2015
- ACM SIGCHI Conference, Seoul, Korea
- AOM Annual Meeting, Vancouver, BC, Canada
- Atlanta Competitive Advantage Conference (ACAC), Atlanta, GA
- DRUID Conference, Rome, Italy
- IEEE VIS Workshop, Chicago, IL
- Industry Studies Association (ISA), Kansas City, MO
- INFORMS Annual Meeting, Philadelphia, PA

## 2014
- INFORMS Annual Meeting, San Francisco, CA
- POMS Annual Meeting, Atlanta, GA
- Systems Engineering Research Center (SERC), Washington, DC

## 2013
- Annual Conference on Internet Search and Innovation, Northwestern University, Chicago, IL
- Atlanta Competitive Advantage Conference (ACAC), Atlanta, GA
- Computational Social Science Workshop, Emory University, Atlanta, GA
- Georgia Tech Research & Innovation Conference, Georgia Tech, Atlanta, GA
- INFORMS Annual Meeting, Minneapolis, MN
- NET Institute Conference, Berkeley, CA
- Southern Economic Association Conference, Tampa, FL
- Strategic Management Society Conference, Atlanta, GA


# Other Research and Professional Experience
\vspace{.5em}
- **Vanderbilt University Medical Center**, Nashville, TN (Summer 2012): _Visiting Researcher_
- **IBM Research**, Bangalore, India (Summer 2010): _Summer Intern_
- **UC Berkeley**, Berkeley, CA (Spring 2010): _Graduate Student Researcher_ for Prof. Morten T. Hansen
- **UC Berkeley**, Berkeley, CA (2009): _Graduate Student Researcher_ for Prof. Robert G. Glushko
- **Samsung Electronics**, Seoul, Korea (2005-2008): _Summer Intern and Part-time Student Research Assistant_ at Corporate Design Center
- **United States Forces Korea**, Seoul, Korea (2003-2005): _Web Developer_ (Obligatory Military Service)



# Software
\vspace{.5em}
- **JSON-based Academic Homepage Template**: https://github.com/oksure/hyunwoopark-com
- **Simple Network Viewer**: https://hyunwoopark.com/netview/
- **Bicentric Diagrams**: http://bicentric.herokuapp.com/
- **Visual Supply Chain Management**: http://visualscm.herokuapp.com/
- **ecoxight** (Business Ecosystem Intelligence System): https://ecoxight.com/

